### 2012-02-09 trunk/GUIErrorDetector/paper/evaluation.tex
Fix fonts on curly braces in tt font.

\begin{figure}[t]
\hspace{4mm}\small{In class: com.tomczarniecki.s3.gui.DeleteBucketAction}
\vspace{-2mm}
\begin{CodeOut}
\begin{alltt}
59.private void deleteBucket() \{
60.    executor.execute(new Runnable() \{
61.        public void run() \{
62.            try \{
63.                controller.deleteCurrentBucket();
64.            \} catch (Exception e) \{
65.                logger.info("Delete failed", e);
66.                deleteError(); 
67.            \}
68.       \}
69.    \});
70.\}

77.private void deleteError() \{
78.    String text = "Cannot delete folder .....";
79.    display.showErrorMessage("Delete failed", 
        String.format(text, controller.getSelectedBucketName())); 
80.\}
\smallstep
\end{alltt}
\end{CodeOut}
\smallstep
\vspace*{-2.0ex} \Caption{{\label{fig:swingerror} An
invalid thread access error reported by our tool
in the S3dropbox Swing application. The error occurs when
the method \CodeIn{deleteCurrentBucket} invoked on line 63 throws
an exception, which causes method \CodeIn{deleteError} to
access a Swing GUI object \CodeIn{display} on line 79 from
a non-UI thread. This error is previously unknown, and has been confirmed by the S3dropbox developers.
}} %\vspace{-5mm}
\end{figure}

@@

\begin{figure}[t]
\hspace{4mm}\small{In class: com.eclipserunner.views.impl.RunnerView}
\vspace{-2mm}
\begin{CodeOut}
\begin{alltt} 
179.private void initializeResourceChangeListener() \{
180.  ResourcesPlugin.getWorkspace().addResourceChangeListener(
        new IResourceChangeListener() \{
181.      public void resourceChanged(IResourceChangeEvent event) \{
182.        refresh();
183.      \}
184.  \}, IResourceChangeEvent.POST\_CHANGE);
185.\}

414.public void refresh() \{
415.  getViewer().refresh();
416.\}
\end{alltt}
\end{CodeOut}
\smallstep
\vspace*{-2.0ex} \Caption{{\label{fig:pluginerror} An
invalid thread access error reported by our tool
for the EclipseRunner plugin. In Eclipse, the
callback method \CodeIn{resourceChanged} on line 181
is invoked by non-UI threads when a \CodeIn{ResourceChangeEvent}
happens. However, the \CodeIn{refresh} method directly accesses
GUI objects (to refresh the view on line 415) without any
protection and thus triggers the error.
This error has been reported by other users 13 months after the
buggy code was checked in, and fixed by developers.
}} %\vspace{-5mm}
\end{figure}

@@

{\vspace{2mm}
\hspace{3mm}\small{In class: com.google.android.apps.mytracks.StatsUtilities}
\vspace{-2mm}
\begin{CodeOut}
\begin{alltt}
97.  public void setLatLong(int id, double d) \{
98.     TextView msgTextView = (TextView) activity.\textbf{findViewById}(id);
99.     msgTextView.setText(LAT\_LONG\_FORMAT.format(d));
100. \}
\end{alltt}
\end{CodeOut}}

>>>>

\begin{figure}[t]
\hspace{4mm}\small{In class: com.tomczarniecki.s3.gui.DeleteBucketAction}
\vspace{-2mm}
\begin{CodeOut}
\begin{alltt}
59.private void deleteBucket() \ttlcb
60.    executor.execute(new Runnable() \ttlcb
61.        public void run() \ttlcb
62.            try \ttlcb
63.                controller.deleteCurrentBucket();
64.            {\ttrcb} catch (Exception e) \ttlcb
65.                logger.info("Delete failed", e);
66.                deleteError(); 
67.            \ttrcb
68.       \ttrcb
69.    \ttrcb);
70.\ttrcb

77.private void deleteError() \ttlcb
78.    String text = "Cannot delete folder .....";
79.    display.showErrorMessage("Delete failed", 
        String.format(text, controller.getSelectedBucketName())); 
80.\ttrcb
\smallstep
\end{alltt}
\end{CodeOut}
\smallstep
\vspace*{-2.0ex} \Caption{{\label{fig:swingerror} An
invalid thread access error reported by our tool
in the S3dropbox Swing application. The error occurs when
the method \CodeIn{deleteCurrentBucket} invoked on line 63 throws
an exception, which causes method \CodeIn{deleteError} to
access a Swing GUI object \CodeIn{display} on line 79 from
a non-UI thread. This error is previously unknown, and has been confirmed by the S3dropbox developers.
}} %\vspace{-5mm}
\end{figure}

@@

\begin{figure}[t]
\hspace{4mm}\small{In class: com.eclipserunner.views.impl.RunnerView}
\vspace{-2mm}
\begin{CodeOut}
\begin{alltt} 
179.private void initializeResourceChangeListener() \ttlcb
180.  ResourcesPlugin.getWorkspace().addResourceChangeListener(
        new IResourceChangeListener() \ttlcb
181.      public void resourceChanged(IResourceChangeEvent event) \ttlcb
182.        refresh();
183.      \ttrcb
184.  \ttrcb, IResourceChangeEvent.POST\_CHANGE);
185.\ttrcb

414.public void refresh() \ttlcb
415.  getViewer().refresh();
416.\ttrcb
\end{alltt}
\end{CodeOut}
\smallstep
\vspace*{-2.0ex} \Caption{{\label{fig:pluginerror} An
invalid thread access error reported by our tool
for the EclipseRunner plugin. In Eclipse, the
callback method \CodeIn{resourceChanged} on line 181
is invoked by non-UI threads when a \CodeIn{ResourceChangeEvent}
happens. However, the \CodeIn{refresh} method directly accesses
GUI objects (to refresh the view on line 415) without any
protection and thus triggers the error.
This error has been reported by other users 13 months after the
buggy code was checked in, and fixed by developers.
}} %\vspace{-5mm}
\end{figure}

@@

{\vspace{2mm}
\hspace{3mm}\small{In class: com.google.android.apps.mytracks.StatsUtilities}
\vspace{-2mm}
\begin{CodeOut}
\begin{alltt}
97.  public void setLatLong(int id, double d) \ttlcb
98.     TextView msgTextView = (TextView) activity.\textbf{findViewById}(id);
99.     msgTextView.setText(LAT\_LONG\_FORMAT.format(d));
100. \ttrcb
\end{alltt}
\end{CodeOut}}

### 2012-02-09 trunk/GUIErrorDetector/paper/introduction.tex
some tweak on space
Fix fonts on curly braces in tt font.

\smallstep

@@

Take the popular Standard Widget Toolkit (SWT) GUI framework as an example. 
The invalid thread access error is one of the top 3 bugs in developing a SWT application, and is
the source of many relevant concurrency bugs~\cite{top3bugs}.
A Google search for ``SWTException:Invalid thread access''  returns over 11,800 entries,
consisting of numerous bug reports, forum posts, and mailing list threads on
this problem. Eclipse, the IDE for Java development, is built on top of SWT.
Searching for ``SWTException:Invalid thread access'' in Eclipse's bug repository
and discussion forum returns over 2732 bug reports and 351 distinct threads, respectively. 
We manually studied all 156 distinct \textit{confirmed} bug reports, and 
found this error has been reported in at least 20 distinct Eclipse projects
and 40 distinct Eclipse components. Even after over 10 years of active development,
a recent release of Eclipse still contains this error (bug id: 333533, reported in 01/2011).
 In addition, the invalid thread access error
is severe. It is user-perceivable; it cannot be recovered by the program itself,
and it often terminates the whole application. In many circumstances as described in the bug reports,
users can only restart the application to recover from the error.
Furthermore, many reported  errors are non-trivial to diagnose and fix.
Developers usually need non-local reasoning to find the specific
UI interactions that can trigger the bug;  it took developers 2 years
to fix bug 51757 and verify the patch.

\begin{figure}[t]
\hspace{6mm}\small{In class: org.mozilla.gecko.gfx.LayerView}
\vspace{-2mm}
\begin{CodeOut}
\begin{alltt}
68.  public LayerView(Context context, LayerController controller) \{
69.     super(context);
        ....
73.     mRenderer = new LayerRenderer(this);
74.     setRenderer(mRenderer);
        ...
     \}
\end{alltt}
\end{CodeOut}
\hspace{6mm} \small{In Android library class: android.opengl.GLSurfaceView}
\vspace{-2mm}
\begin{CodeOut}
\begin{alltt}
272. public void setRenderer(Renderer renderer) \{
        ...
282.    mGLThread = new GLThread(renderer);
283.    mGLThread.start();   
     \}
\end{alltt}
\end{CodeOut}
 \hspace{6mm}\small{In class: org.mozilla.gecko.gfx.LayerRenderer}
\vspace{-2mm}
\begin{CodeOut}
\begin{alltt}
220. public void onSurfaceChanged(GL10 gl, int width, int height) \{
221.    gl.glViewport(0, 0, width, height);
222.    mView.setViewportSize(new IntSize(width, height));
     \}
\end{alltt}
\end{CodeOut}
\tinystep
\vspace*{-3.0ex} \Caption{{\label{fig:androiderror} 
Bug 703256 reported on 11/17/2011 in Fennec (Mozilla Firefox for Android)
release 10.0.a.rc3. On line 74, \CodeIn{LayerView}'s constructor
calls method \CodeIn{setRenderer} which 
spawns a new thread on line 283. This newly created, non-UI thread calls back method
\CodeIn{onSurfaceChanged} that accesses GUI objects on line 222,
causing an invalid thread access error. Our tool
finds this error and generates a report as shown in
Figure~\ref{fig:report}.
}} %\vspace{-5mm}
\end{figure}

@@

{\vspace{2mm}
\hspace{3mm}\small{In class: org.mozilla.gecko.gfx.LayerRenderer}
\vspace{-2mm}
\begin{CodeOut}
\begin{alltt}
220. public void onSurfaceChanged(GL10 gl, int width, int height) \{
221.     gl.glViewport(0, 0, width, height);
         \textbf{mView.post(new Runnable() \ttlcb}
             \textbf{public void run() \ttlcb}
222.             mView.setViewportSize(new IntSize(width, height));
             \textbf{\ttrcb}
         \textbf{\ttrcb);}
     \}
\end{alltt}
\end{CodeOut}}

>>>>

@@

Take the popular Standard Widget Toolkit (SWT) GUI framework as an example. 
The invalid thread access error is one of the top 3 bugs in developing a SWT application, and is
the source of many relevant concurrency bugs~\cite{top3bugs}.
A Google search for ``SWTException:Invalid thread access''  returns over 11,800 entries,
consisting of numerous bug reports, forum posts, and mailing list threads on
this problem. Eclipse, the IDE for Java development, is built on top of SWT\@.
Searching for ``SWTException:Invalid thread access'' in Eclipse's bug repository
and discussion forum returns over 2732 bug reports and 351 distinct threads, respectively. 
We manually studied all 156 distinct \textit{confirmed} bug reports, and 
found this error has been reported in at least 20 distinct Eclipse projects
and 40 distinct Eclipse components. Even after over 10 years of active development,
a recent release of Eclipse still contains this error (bug id: 333533, reported in 01/2011).
 In addition, the invalid thread access error
is severe. It is user-perceivable; it cannot be recovered by the program itself,
and it often terminates the whole application. In many circumstances as described in the bug reports,
users can only restart the application to recover from the error.
Furthermore, many reported  errors are non-trivial to diagnose and fix.
Developers usually need non-local reasoning to find the specific
UI interactions that can trigger the bug;  it took developers 2 years
to fix bug 51757 and verify the patch.

\begin{figure}[t]
\hspace{6mm}\small{In class: org.mozilla.gecko.gfx.LayerView}
\vspace{-2mm}
\begin{CodeOut}
\begin{alltt}
68.  public LayerView(Context context, LayerController controller) \ttlcb
69.     super(context);
        ....
73.     mRenderer = new LayerRenderer(this);
74.     setRenderer(mRenderer);
        ...
     \ttrcb
\end{alltt}
\end{CodeOut}
\hspace{6mm} \small{In Android library class: android.opengl.GLSurfaceView}
\vspace{-2mm}
\begin{CodeOut}
\begin{alltt}
272. public void setRenderer(Renderer renderer) \ttlcb
        ...
282.    mGLThread = new GLThread(renderer);
283.    mGLThread.start();   
     \ttrcb
\end{alltt}
\end{CodeOut}
 \hspace{6mm}\small{In class: org.mozilla.gecko.gfx.LayerRenderer}
\vspace{-2mm}
\begin{CodeOut}
\begin{alltt}
220. public void onSurfaceChanged(GL10 gl, int width, int height) \ttlcb
221.    gl.glViewport(0, 0, width, height);
222.    mView.setViewportSize(new IntSize(width, height));
     \ttrcb
\end{alltt}
\end{CodeOut}
\tinystep
\vspace*{-3.0ex} \Caption{{\label{fig:androiderror} 
Bug 703256 reported on 11/17/2011 in Fennec (Mozilla Firefox for Android)
release 10.0.a.rc3. On line 74, \CodeIn{LayerView}'s constructor
calls method \CodeIn{setRenderer} which 
spawns a new thread on line 283. This newly created, non-UI thread calls back method
\CodeIn{onSurfaceChanged} that accesses GUI objects on line 222,
causing an invalid thread access error. Our tool
finds this error and generates a report as shown in
Figure~\ref{fig:report}.
}} %\vspace{-5mm}
\end{figure}

@@

{\vspace{2mm}
\hspace{3mm}\small{In class: org.mozilla.gecko.gfx.LayerRenderer}
\vspace{-2mm}
\begin{CodeOut}
\begin{alltt}
220. public void onSurfaceChanged(GL10 gl, int width, int height) \ttlcb
221.     gl.glViewport(0, 0, width, height);
         \textbf{mView.post(new Runnable() \ttlcb}
             \textbf{public void run() \ttlcb}
222.             mView.setViewportSize(new IntSize(width, height));
             \textbf{\ttrcb}
         \textbf{\ttrcb);}
     \ttrcb
\end{alltt}
\end{CodeOut}}
